---
title: Detailed EWAS report
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
pkgs <- c("knitr", "pander")
lapply(pkgs, require, character.only = TRUE)

knitr::opts_chunk$set(echo = FALSE, 
            warning = FALSE, 
            message = TRUE, 
            cache = FALSE, 
            dpi = 300 
            )

# Function for numbers in rmarkdown
comma <- function(x) format(x, digits = 2, big.mark = ",")

# Function for printing if object exists
print_if_exists <- function(object) {
	obj_nam <- deparse(substitute(object))
	if (exists(obj_nam)) {
		return(object)
	} else {
		print(paste(obj_nam, "isn't present"))
	}
}
```

## Checklist

1. Range of summary statistics are reasonable, e.g. standard errors aren't all above 1000.
2. Number of associations are reasonable.
3. The EFO term is present. This will need to be filled in if not.
4. Array entered and number of rows in results matches.
5. If trait has well established cpg-trait associations, they are present in top hits (e.g. cg05575921 is present for smoking EWAS).

## Summary of results

* P-value range: `r paste(comma(range(full_results$P)), collapse = ", ")`
* N sites with P<1e-7: `r n_p7`
* N sites with P<1e-4: `r n_p4`
* SE range is `r range(full_results$SE)`
* Number of effect estimate outliers: `r length(beta_out)`
* EFO term is present: `r !is.na(studies$EFO)`
* Array: `r studies$Methylation_Array`
* Rows in results: `r nrow(results)` 

## P-values

Here is a look at the top 10 strongest associations in your results (ordered by p-value):

```{r results-check, results="asis"}
pander(top_hits)
```

```{r man-plot, results="asis"}
print_if_exists(manhattan.plot)
```

```{r qq-plot, results="asis"}
print_if_exists(qq.plot)
```

## Beta + SE distributions

```{r beta-histogram, results="asis"}
if (betas_present) hist(full_results$Beta)
```

```{r se-histogram, results="asis"}
if (se_present) hist(full_results$SE)
```
